---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MAJAR
*Yuhan Xie, Song Zhai, Wei Jiang, Hongyu Zhao, Devan V. Mehrotra, Judong Shen*            
<!-- badges: start -->
<!-- badges: end -->

We propose MAJAR (Meta-Analysis of Joint effect Associations for biomarker Replicability assessment) to jointly test prognostic and predictive effects in meta-analysis without the need of using an independent cohort for replication of the detected biomarkers. MAJAR builds upon a two-dimensional hierarchical mixture model and adopts an efficiently-implemented Expectation-Maximization (EM) algorithm for parameter estimation. It provides posterior probabilities of replicability (PPRs) and Bayesian false discovery rates (Fdr) for all biomarkers tested.

## Source 

To install the software for *MAJAR*, you need package *devtools* first

```{R}
if (!requireNamespace("devtools", quietly = TRUE))
    install.packages("devtools")
library(devtools)
```

Then, you can install *MAJAR* 
```{R}
install_github("JustinaXie/MAJAR")
```

```{R}
Rcpp::sourceCpp("src/file.cpp")
source("R/MAJAR.R")
source("R/Simulation.R")
```

## Example

This is a basic example which shows you how to solve a common problem:


1. An example of simulation under MAJAR's data generation process. 
```{r settings}
M_real = 1000
K_real = 5
p_real =0.1
h2_real = 0.1
rho_real = 0.5
alpha_real = 2
data_real = "random" 
DGP = "MAJAR"
lambda_real = 0.1
data_simu_mamba_PGx<-generate_data_DGP(M=M_real,K=K_real,
                                       p=p_real,
                                       data=data_real,
                                       h2=h2_real,
                                       alpha=alpha_real,
                                       lambda = lambda_real,
                                       rho=rho_real,
                                       model = DGP)
betajk_G<-data_simu_mamba_PGx$betajk_G
betajk_GT<-data_simu_mamba_PGx$betajk_GT
sjk2_G<-data_simu_mamba_PGx$sjk2_G
sjk2_GT<-data_simu_mamba_PGx$sjk2_GT
```

2. Run MAJAR. 
```{r MAJAR}
MAJAR_results<-MAJAR(betajk_G, sjk2_G, 
                                     betajk_GT, sjk2_GT,
                                     p=0.1,#Rj~Bernoulli(pi)
                                     lambda=0.1,#Ojk~Bernoulli(lambda)
                                     tau2=0.001,
                                     alpha=1,
                                     rho=0,
                                     parcores = 4,
                                     minIter = 100,
                                     maxIter=1e4,
                                     tmp=10^6,
                                     transform=TRUE,
                                     fast_implement=TRUE)
```

3. Check the results of MAJAR
```{r results}
hist(MAJAR_results$ppr)
```

```{r estimation}
print(paste0("The estimated replicable non-zero effect proportion:",round(MAJAR_results$p,3)))
print(paste0("The estimated outlier proportion:",round(MAJAR_results$lambda,3)))
print(paste0("The estimated inflation rate factor:",round(MAJAR_results$alpha,3)))
print(paste0("The estimated heritability:",round(MAJAR_results$h2,3)))
print(paste0("The estimated correlation between main and interaction effect:",round(MAJAR_results$rho,3)))
```

```{r time}
MAJAR_results$Time
```

